\begin{abstract}

In the big data era, the data-driven fight against organized crime is opening new research challenges and directions.
%
In particular, the real-time discovery of hidden and potential patterns in criminal interactions are outstanding tasks for security and law enforcement agencies. 
%
In fact, uncovering concealed relationships and predicting the evolution of criminal networks  can efficiently guide investigations for better decision-making and territory control.

Traditionally, these tasks are addressed analysing a restricted part of a massive dataset with an occasional offline approach. These systems can not provide a real-time insights of the overall criminal scenario. 

Today, models and technologies of big data analytics can disruptively reshape the core of these tasks providing the permanent live monitoring of the whole criminal network. 

In this work we propose three new similarity social network metrics for criminal link detection and prediction, with their data stream processing implementation. These metrics are modelled both domain-aware and ready to be executed in a data stream environment.
%
Furthermore, determining the best metric for specific criminal datasets is not an easy task. For this reason we propose a flexible data stream processing architecture, that makes really easy to deploy and analyze these metrics.

The experiments are aimed at comparing classical similarity metrics with the proposed ones in detecting and predicting criminal patterns. The experimental results show that the new metrics we propose can reach up to \hlr{??\%} accuracy in detection, and \hlr{??\%} accuracy in prediction.
\end{abstract}
