\begin{abstract}
	
The ability to discover patterns of interest in criminal networks can support and ease the investigation tasks by security and law enforcement agencies. 
%
Being the criminal network a special case of social network, we can properly reuse most of the state-of-the-art techniques to discover patterns of interests, i.e., hidden and potential links. 
%
Nevertheless, in time-sensible scenarios, like the one involving criminal actions, the ability to discover patterns in a (near) real-time manner can be of primary importance. 

In this paper, we investigate the identification of patterns for link detection and prediction on an evolving criminal network. 
Being the criminal network a dynamic social graph, we exploit a stream processing approach to extract information of interest as soon as data is generated.
To this end, we also propose three new similarity social network metrics, specifically tailored for criminal link detection and prediction.
Then, we develop a flexible data stream processing application, relying on the framework Apache Flink;
this solution allows to deploy and evaluate the newly proposed metrics as well as the one existing in literature. 
	%
The experimental results show that the new metrics we propose can reach up to 83\% accuracy in detection and 82\% accuracy in prediction, resulting competitive with the state of the art metrics.

% OLD: START
%In the Big Data era, the data-driven fight against organized crime is opening new research challenges and directions.
%In particular, the real-time discovery of hidden and potential patterns in criminal interactions are outstanding tasks for security and law enforcement agencies.

%Traditionally, these tasks are addressed analyzing a restricted part of a massive dataset with an occasional offline approach. 
%These systems can not provide a real-time insights of the overall criminal scenario. 

%Today, models and technologies of big data analytics can disruptively reshape the core of these tasks providing the permanent live monitoring of the whole criminal network. 

%In this work we propose three new similarity social network metrics for criminal link detection and prediction, with their data stream processing implementation. 
%These metrics are modelled both domain-aware and ready to be executed in a data stream environment.
%Furthermore, determining the best metric for specific criminal datasets is not an easy task. 
%For this reason we propose a flexible data stream processing architecture, that makes really easy to deploy and analyze these metrics.
%The experiments are aimed at comparing classical similarity metrics with the proposed ones in detecting and predicting criminal patterns. 
%The experimental results show that the new metrics we propose can reach up to 83\% accuracy in detection, and 82\% accuracy in prediction.
% OLD: END

\end{abstract}
